### 2021-02-02 research project/sections/Analysis_of_results.tex
""

@@

To better show the trend in the data collected, the data 
has been presented in a scatter chart below. The blue markers and line of best-fit 
respresent the results received from Viète's method while the red represent those 
from Madhava's method.

@@

@@

The results gathered from this experiment show linear relationship between the amount of decimal 
places approximated and the time required for this approximation. The two lines of best fit for 
the two methods show similarities but also differences. It can be firstly noted that Madhava's 
method is faster than the other until the decimal 20, when the two best fit lines diverge. This 
can be explained as due to the convergence rates of the two methods, which can be seen in (Figure 3) 
\ref{fig:comparaison}. In the beginning of this curve representing the convergence of Viète's method, 
it cna be seen that it does not follow an \textit{alternating} method, like the one formulated by 
Madhava. Madhava's method is what is called an alternating series, in this case one that converges 
to the value $\pi$ \footnote{Note: not all alternating series converge}

\begin{figure}
    \includegraphics[width=\linewidth]{image.png}
    \caption{Comparison of historical methods of approximating the value of $\pi$. This image demonstrates
    their convergence rates. The line labelled Madhava in dark blue is the method used in this paper. 
    From (Wikimedia Commons) \cite{infinite_series_comparaison}}
    \label{fig:comparaison}
  \end{figure}

>>>>

\begin{table}[h]
    \noindent% <-- important
    \setlength\tabcolsep{3pt} % default: 6pt
    \begin{tabularx}{\textwidth}{@{} l *{6}{C} @{}}
    \toprule
    Decimal place & Iterations needed, Viète's method (no unit) & Iterations needed, Madhava's method (no unit)\\
    \midrule
    5 & 10 & 9 \\
    10 & 17 & 20 \\
    15 & 27 & 29 \\
    20 & 35 & 41 \\
    25 & 42 & 50 \\
    30 & 51 & 61 \\
    35 & 59 & 71 \\
    40 & 67 & 82 \\
    45 & 76 & 91 \\
    50 & 84 & 102 \\
    55 & 92 & 112 \\
    60 & 101 & 123
    \end{tabularx}
\end{table}

The iterations needed for both methods were also measured, using the Python program 
(see appendix), slightly modified to increment a variable \verb|i| and subsequently 
return it, writing it in a similar manner to a \verb|.csv| file.

@@

To better show the trend in the data collected, see below the decimal places compared 
to the time taken per method. The blue markers and line of best-fit 
respresent the results received from Viète's method while the red represent those 
from Madhava's method. \\

@@

Include Decimal places vs Iterations

@@

The results gathered from this experiment show linear relationship between the amount of decimal 
places approximated and the time required for this approximation. The two lines of best fit for 
the two methods show similarities but also differences. It can be firstly noted that Madhava's 
method is faster than the other until the decimal 20, when the two best fit lines diverge. This 
can be explained as due to the convergence rates of the two methods, which can be seen in (Figure 3) 
\ref{fig:comparaison}. In the beginning of this curve representing the convergence of Viète's method, 
it can be seen that it does not follow an \textit{alternating} method, like the one formulated by 
Madhava. Madhava's method is what is called an alternating series, in this case one that converges 
to the value $\pi$, and as such it is closer to the correct value of $\pi$ at lower decimal values 
and gradually takes longer and longer than Viète's method, which is an infinite product. This difference 
in speeds can be attributed to the fact that

\begin{figure}[h]
    \includegraphics[width=\linewidth]{image.png}
    \caption{Comparison of historical methods of approximating the value of $\pi$. This image demonstrates
    their convergence rates. The line labelled Madhava in dark blue is the method used in this paper. 
    From (Wikimedia Commons) \cite{infinite_series_comparaison}}
    \label{fig:comparaison}
  \end{figure}
